THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-23 DishReflectometry/Paper1_v1.tex
Fixed some spelling issues

\author{Nipanjana Patra\altaffilmark{1} }
\email{Contact author email: nipanjana@berkeley.edu}
\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}}
\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
\altaffiltext{2}{To be inserted}

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

The total reflected power, returned to the VNA, denoted byt $I_{ret}$ would be:
\begin{eqnarray}\label{eqn:series2}
I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
\end{eqnarray}

@@

The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, mutiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.

@@

While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net retrun loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}. This provides the maximum impedance matching. \\

>>>>

\author{Nipanjana Patra\altaffilmark{1} }
\email{Contact author email: nipanjana@berkeley.edu}
\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki S. Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}}
\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
\altaffiltext{2}{To be inserted}

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

The total reflected power, returned to the VNA, denoted by $I_{ret}$ would be:
\begin{eqnarray}\label{eqn:series2}
I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
\end{eqnarray}

@@

The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.

@@

While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}. This provides the maximum impedance matching. \\
